StreamReduce: Processing Data Streams\\and Avoiding Work

### 2012-05-10 paper/paper.tex
clarify aurora operators
Rework introduction

\usepackage{fullpage}
\usepackage{listings}
\usepackage{graphicx}
\graphicspath{{images/}}
\usepackage{tabularx}
\usepackage{url}

\title{StreamReduce: Processing Data Streams\\and Avoiding Work}
\author{Ryan Lopopolo\\
Massachusetts Institute of Technology\\
\texttt{lopopolo@mit.edu}}

@@

\section{Introduction}
\label{sec:intro}
One of the fundamental problems MapReduce was created to solve was processing
the growing amount of data in the world. Now with the open source Apache Hadoop
and Pig~\cite{Olston:2008:PLN:1376616.1376726}, it is easy to process and query
the terabytes of data an organization
may collect. With terabytes of data, however, it is scarcely necessary to examine
every entry to uncover trends, especially when one only cares about the most prominent
trends or results. This type of workflow lends itself naturally to top-k-style computations,
data sampling tasks, and other cases where perfect-fidelity results are not required.
%Google runs PageRank on the entire Internet, but if
%it only did on half of the pages it crawls, it would likely still have a usable
%index for delivering the first 5 pages of results.

How does one decide which data to process then? Selctively deciding which data to
log is problematic because it can systemically mask some of the trends one would
try to uncover through analysis. In this paper, I explore the possibility of
discarding data randomly while trying to maintain a target accuracy level.
On the subset of data that I do process, I explore using
computation routines of differing fidelities to sample the data. Combining both of these
techniques allows the cluster to avoid performing work.

One of the problems with MapReduce is how to
incorporate new data into an already analyzed task. MapReduce simply says to rerun
the job with the new data included. Others have solved this problem by batching data
into chunks and continuously spawning MapReduce jobs to incorporate the new data
and incrementally storing updates in an external database instead of relying on
the file system for enforcing the synchronization barrier.

@@

The goal of StreamReduce is to provide a MapReduce-style framework for processing streams. Such a
framework should include the ability to kill or discard tasks and be capable of
providing workers with serveral different computation routines to choose among.

The remainder of this paper is organized as follows. Section~\ref{sec:relwork} provides
an overview of related work on distributed stream processing as well as dynamic and
approximate computations. Section~\ref{sec:design} details the design of StreamReduce.
Section~\ref{sec:methodology} explains the methodology used to perform a case study
using StreamReduce. Section~\ref{sec:evaluation} evaluates the effectiveness of StreamReduce in the case study.
Section~\ref{sec:discussion} enumerates issues with StreamReduce's current implementation.

@@

Aurora also introduces the operators \texttt{filter}, \texttt{map}, and \texttt{union} for
manipulating streams. StreamReduce implements these operators at the worker and fetcher nodes.

>>>>

\usepackage{fullpage}
\usepackage{listings}
\usepackage{graphicx}
\graphicspath{{images/}}
\usepackage{tabularx}
\usepackage{url}
\usepackage{hyperref}

\title{StreamReduce: Processing Data Streams\\and Avoiding Work}
\author{Ryan Lopopolo\\
Massachusetts Institute of Technology\\
\href{mailto:lopopolo@mit.edu}{\texttt{lopopolo@mit.edu}}}

@@

\section{Introduction}
\label{sec:intro}
One of the fundamental problems MapReduce was created to solve was processing
the growing amount of data in the world.
MapReduce lends itself naturally to top-k-style computations,
data sampling tasks, and other cases where perfect-fidelity results are not required.
Now with the open source Apache Hadoop
and Pig~\cite{Olston:2008:PLN:1376616.1376726}, it is easy to process and query
the terabytes of data an organization may collect.
%The widespread use of these tools to solve problems they weren't designed for motivates
%us to explore how we can save time, resources, and prevent faults in the execution of
%such MapReduce tasks.

With terabytes of data, however, it is scarcely necessary to examine
every entry to uncover trends, especially when one only cares about the most prominent
trends or results.
How does one decide which data to process then? Ultimately, this is problem dependent;
however, selctively deciding which data to
log is problematic because it can systemically mask some of the trends one would
try to uncover through analysis. In this paper, I introduce StreamReduce, a distributed system
for processing data streams. With StreamReduce I explore:
\begin{itemize}
  \item
    Randomly discarding data while trying to maintain a target accuracy level.
  \item
    Processing data using a variety of computation routines, some of which are less
    accurate than others.
\end{itemize}
Combining both of these techniques allows the cluster to save time by executing faster,
save resources by avoiding the need to process every datum, and minimize the impact of faults
in the execution of a job by treating failed tasks as discarded tasks.

Another limitation of MapReduce is batch processing. How does one
incorporate new data into an already analyzed task? MapReduce simply says to rerun
the job with the new data included. Others have solved this problem by batching data
into chunks and continuously spawning MapReduce jobs to incorporate the new data
and incrementally storing updates in an external database instead of relying on
the file system for enforcing the synchronization barrier.

@@

The goal of StreamReduce is to provide a MapReduce-style framework for processing streams. Such a
framework should include the ability to kill or discard tasks, be capable of
providing workers with serveral different computation routines to choose among, and pass data
between nodes using non-blocking routines.

@@

Aurora also introduces the non-blocking operators
\texttt{filter}, \texttt{map}, and \texttt{union} for
manipulating streams. StreamReduce implements these operators at the worker and fetcher nodes.
